The letter

### 2010-06-30 ltx/PLoS/LaTeX_Manuscript.tex
changes to tables

which is a constant $L \times n_{\theta}$ matrix that is defined analytically (see the Supporting Information, S1, for analytic convolution of two Gaussians as given by Equation~\ref{eq:DefPsi}), where $L$ is the number of basis functions (and states) and $n_{\theta}$ is the number of connectivity basis functions. Now substituting equation~\ref{eq:DefPsi} into~\ref{eq:ReducedForm} gives

@@

This simplification has transformed the description of the spatial coupling from a convolution of the firing rates with the connectivity kernel, to a convolution of the connectivity kernel basis functions with the field basis functions. This transformation provides a dramatic increase in estimation speed, since the matrix $\Psi(\mathbf{r}')$ is constant and can be pre-defined analytically. This is of great importance considering the computational demands of the estimation algorithm.

@@

\begin{table}[!ht]
\caption{
\bf{Notation}}
\begin{tabular}{|l|l|l|}
	\hline
	\textbf{Symbol} & \textbf{Quantity} & \textbf{Units}\\
	\hline
	\multicolumn{3}{|c|}{\emph{Domain and indices}}\\
	\hline
	$\Omega$ & spatial domain & n.a.\\
	$\mathbf{r}$ & spatial location & [mm, mm]\\
	$t$ & time & s\\
	\hline
	\multicolumn{3}{|c|}{\emph{Model}}\\
	\hline
    $y(\mathbf{r}_n,t)$ & observation & mV\\
    $v(\mathbf{r},t)$ & mean membrane potential & mV \\
	$g(\mathbf{r},t)$ & weighted firing rate function & spikes.s$^{-1}$\\
	$f(\mathbf{r},t)$ & firing rate function & spikes.s$^{-1}$\\
	$e(\mathbf{r},t)$ & field disturbance, with covariance function $\gamma(\mathbf r-\mathbf r')$ & mV\\
	$\varepsilon(\mathbf{r}_n,t)$ & observation noise, with covariance matrix $\Sigma_\varepsilon$ & mV\\
	$m(\mathbf{r}_n,\mathbf{r}')$ & sensor kernel where $n$ is sensor index $n=1,..,N$ (width $\sigma_m^2$) & n.a. \\
	$w(\mathbf{r},\mathbf{r}')$ & spatial connectivity kernel & n.a.\\
	$h(t)$ & post-synaptic response kernel & mV\\
	$\zeta$ & inverse synaptic time constant & s$^{-1}$\\
	$\xi$ & time constant parameter & n.a.\\
	$\eta(t)$ & Heaviside step function & n.a.\\
	$\delta(t)$ & Dirac-delta function & n.a.\\
	$D$ & temporal differential operator & n.a.\\
	\hline
	\multicolumn{3}{|c|}{\emph{Reduced Model}} \\
	\hline
   	$\boldsymbol\phi(\mathbf{r})$ & vector of $L$ Gaussian basis functions & n.a.\\
   	$\mathbf{x}_t$ & state vector at time $t$ & mV\\
   	$\boldsymbol{\psi}(\mathbf{r}-\mathbf{r}')$ & vector of connectivity kernel basis functions & n.a.\\
   	$\boldsymbol{\Gamma}$ & inner product of field basis functions & n.a.\\
   	$Q()$ & state transition function &\\
   	$\mathbf{e}_t$ & state disturbance vector, with covariance $\Sigma_e$ & mV\\
   	$\mathbf{C}$ & observation matrix & n.a. \\
	\hline
	\multicolumn{3}{|c|}{\emph{Frequency Analysis}} \\
	\hline
    % $V(\nu)$ & Fourier transform of the neural field & Hz\\
	$\boldsymbol{\nu}$, $\boldsymbol{\nu}_c$ & spatial frequency and spatial cut-off frequency & Hz \\
	$\sigma_{\nu}^2$ & Variance of Fourier transformed Gaussian basis function & Hz$^2$\\
	\hline
	\multicolumn{3}{|c|}{\emph{Estimation}} \\
	\hline
	$\mathcal{X}$ & matrix of sigma vectors & mV\\
	$W$ & matrix of sigma vector weights (scaling parameter $\lambda$) & n.a.\\
   	$\hat{\mathbf{x}}_t^{f-}$, $\hat{\mathbf{x}}_t^f$ & forward prior and posterior state estimates & mV\\
   	$\hat{\mathbf{x}}_t^{b-}$, $\hat{\mathbf{x}}_t^{b}$ & backward prior and posterior state estimates & mV\\
 	$P^{f-}_t$, $P^f_t$  & forward prior and posterior covariance matrices & mV$^2$\\
   	$P^{b-}_t$, $P^b_t$ & backward prior and posterior covariance matrices & mV$^2$\\
	$M_t$& cross-covariance matrix & mV$^2$\\
	$\mathcal K_{t} $ & filter gain & n.a.\\
	$S_t$ & smoother gain & n.a.\\
	$q()$ & parameterised nonlinear state function (used in LS estimator) & n.a.\\
   	$\mathcal{\hat{W}}$& vector of parameter estimates (used in LS estimator) & n.a.\\	
	\hline
\end{tabular}
\begin{flushleft}The first column of the table gives the symbols for all the notation used the paper. The second column provides a brief description of the quantity, and the third column provides the SI units where relevant.
\end{flushleft}
\label{tab:Notation}
\end{table}

@@

\begin{table}[!ht]
\caption{
\bf{Parameters}}
\begin{tabular}{|c|l|c|l|}
	\hline
	\textbf{Symbol} & \textbf{Quantity} & \textbf{Value} & \textbf{Units}\\
	\hline
	\multicolumn{4}{|c|}{\emph{Domain and indices}}\\
	\hline
	$\Delta$ & spatial discretisation step & 0.5 & mm \\
	$T_s$ & time step & $0.001$ & s\\
	$T$ & number of time steps used in estimation & 0.4 & s\\
	\hline 
\multicolumn{4}{|c|}{\emph{Model}}\\
	\hline
	$\tau$ & synaptic time constant & 0.01 & s$^{-1}$ \\
	$f_{max}$ & maximal firing rate & 10 & spikes.s$^{-1}$\\
	$\varsigma$ & slope of sigmoidal activation function & 0.8 & mV$^{-1}$\\
	$v_0$ & firing threshold & 2 & mV \\
	$\boldsymbol{\theta}$ & vector of connectivity kernel parameters & $\left[\begin{array}{ccc}
	10 &-8 &0.5
	\end{array}
	\right]^{\top}$ & mV.spike$^{-1}$\\
	$\sigma_{\psi_{1}}, \sigma_{\psi_{2}}, \sigma_{\psi_{3}}$ & connectivity kernel width parameters & 1.8, 2.4, 6 & mm\\
	$\Delta_y$ & distance between adjacent sensors & 1.5 & mm\\
	$\sigma_{m}$ & sensor width parameter & 0.9 & mm \\
	$\Sigma_{\varepsilon}$ & observation noise variance & $0.1 \times I_{N}$ & mm$^2$ \\
	$\sigma_{\gamma}$& disturbance spatial covariance width & 1.3 & mm\\
	$\sigma_{\gamma,t}$ & disturbance temporal variance & 0.1 & mV \\
	\hline 
	\multicolumn{4}{|c|}{\emph{Reduced Model}}\\
	\hline
	$\Delta_{\phi}$ & Distance between field basis functions & 2.5 & mm \\
	$\sigma^2_{\phi}$ & Spatial variance of Gaussian in spatial domain & 2.5 & mm$^2$\\
	\hline 
	\multicolumn{4}{|c|}{\emph{Frequency Analysis}}\\
	\hline
	$\rho_y$ & Sensor over-sampling parameter & 1 & n.a.\\
	$\rho_\phi$ & Field basis function over-sampling parameter & 1 & n.a.\\
	\hline 
	\multicolumn{4}{|c|}{\emph{Estimation}}\\
	\hline
	$\alpha$& Determines the spread of sigma points & 0.001 & n.a.\\
	$\beta$& Prior knowledge of the sigma points distribution & 2 & n.a.\\
	$\kappa$& Scaling parameter & $3-L$ & n.a.\\
	\hline
\end{tabular}
\begin{flushleft}Parameters for the neural field model, the model reduction, the frequency analysis and the estimation procedure.
\end{flushleft}
\label{tab:Parameters}
\end{table}

>>>>

which is a constant $L \times n_{\theta}$ matrix that is defined analytically (see the Supporting Information, S1, for analytic convolution of two Gaussians as given by Equation~\ref{eq:DefPsi}), where $L$ is the number of basis functions (and states) and $n_{\theta}$ is the number of connectivity kernel basis functions. Now substituting equation~\ref{eq:DefPsi} into~\ref{eq:ReducedForm} gives

@@

This simplification has transformed the description of the spatial coupling from a convolution of the firing rates with the connectivity kernel, to a convolution of the connectivity kernel basis functions with the field basis functions. This transformation provides a dramatic increase in estimation speed, since the matrix $\boldsymbol\Psi(\mathbf{r}')$ is constant and can be pre-defined analytically. This is of great importance considering the computational demands of the estimation algorithm.

@@

\begin{table}[!ht]
\caption{
\bf{Notation}}
\begin{tabular}{|l|l|l|}
	\hline
	\textbf{Symbol} & \textbf{Quantity} & \textbf{Units}\\
	\hline
	\multicolumn{3}{|c|}{\emph{Domain and indices}}\\
	\hline
	$\Omega$ & spatial domain & n.a.\\
	$\mathbf{r}$ & spatial location & [mm, mm]\\
	$t$ & time & s\\
	\hline
	\multicolumn{3}{|c|}{\emph{Model}}\\
	\hline
    $y_t$ & observation & mV\\
    $v(\mathbf{r},t)$ & mean membrane potential & mV \\
	$g(\mathbf{r},t)$ & weighted firing rate function & spikes.s$^{-1}$\\
	$f(\mathbf{r},t)$ & firing rate function & spikes.s$^{-1}$\\
	$e(\mathbf{r},t)$ & field disturbance, with covariance function $\gamma(\mathbf r-\mathbf r')$ & mV\\
	$\varepsilon_t$ & observation noise, with covariance matrix $\Sigma_\varepsilon$ & mV\\
	$m(\mathbf{r}_n,\mathbf{r}')$ & sensor kernel where $n$ is sensor index $n=1,..,N$ (width $\sigma_m^2$) & n.a. \\
	$w(\mathbf{r},\mathbf{r}')$ & spatial connectivity kernel & n.a.\\
	$h(t)$ & post-synaptic response kernel & mV\\
	$\zeta$ & inverse synaptic time constant & s$^{-1}$\\
	$\xi$ & time constant parameter & n.a.\\
	$\eta(t)$ & Heaviside step function & n.a.\\
	$\delta(t)$ & Dirac-delta function & n.a.\\
	$D$ & temporal differential operator & n.a.\\
	\hline
	\multicolumn{3}{|c|}{\emph{Reduced Model}} \\
	\hline
   	$\boldsymbol\phi(\mathbf{r})$ & vector of $L$ Gaussian basis functions & n.a.\\
   	$\mathbf{x}_t$ & state vector at time $t$ & mV\\
   	$\boldsymbol{\psi}(\mathbf{r}-\mathbf{r}')$ & vector of connectivity kernel basis functions & n.a.\\
	$n_{\theta}$ & number of connectivity kernel basis functions & n.a.\\
   	$\boldsymbol{\Psi}(\mathbf{r}')$ & scaled convolution of the connectivity kernel basis functions with the field basis functions& n.a.\\
   	$\boldsymbol{\Gamma}$ & inner product of field basis functions & n.a.\\
   	$Q()$ & state transition function & n.a.\\
   	$\mathbf{e}_t$ & state disturbance vector, with covariance $\Sigma_e$ & mV\\
   	$\mathbf{C}$ & observation matrix & n.a. \\
	\hline
	\multicolumn{3}{|c|}{\emph{Frequency Analysis}} \\
	\hline
    % $V(\nu)$ & Fourier transform of the neural field & Hz\\
	$\boldsymbol{\nu}$, $\boldsymbol{\nu}_c$ & spatial frequency and spatial cut-off frequency & Hz \\
	$\sigma_{\nu}^2$ & variance of Fourier transformed Gaussian basis function & Hz$^2$\\
	\hline
	\multicolumn{3}{|c|}{\emph{Estimation}} \\
	\hline
	$\mathcal{X}$ & matrix of sigma vectors & mV\\
	$W$ & matrix of sigma vector weights (scaling parameter $\lambda$) & n.a.\\
   	$\hat{\mathbf{x}}_t^{f-}$, $\hat{\mathbf{x}}_t^f$ & forward prior and posterior state estimates & mV\\
   	$\hat{\mathbf{x}}_t^{b-}$, $\hat{\mathbf{x}}_t^{b}$ & backward prior and posterior state estimates & mV\\
 	$P^{f-}_t$, $P^f_t$  & forward prior and posterior covariance matrices & mV$^2$\\
   	$P^{b-}_t$, $P^b_t$ & backward prior and posterior covariance matrices & mV$^2$\\
	$M_t$& cross-covariance matrix & mV$^2$\\
	$\mathcal K_{t} $ & filter gain & n.a.\\
	$S_t$ & smoother gain & n.a.\\
	$q()$ & parameterised nonlinear state function (used in LS estimator) & n.a.\\
   	$\mathcal{\hat{W}}$& vector of parameter estimates (used in LS estimator) & n.a.\\	
	\hline
\end{tabular}
\begin{flushleft}The first column of the table gives the symbols for all the notation used the paper. The second column provides a brief description of the quantity, and the third column provides the SI units where relevant.
\end{flushleft}
\label{tab:Notation}
\end{table}

@@

\begin{table}[!ht]
\caption{
\bf{Parameters}}
\begin{tabular}{|c|l|c|l|}
	\hline
	\textbf{Symbol} & \textbf{Quantity} & \textbf{Value} & \textbf{Units}\\
	\hline
	\multicolumn{4}{|c|}{\emph{Domain and indices}}\\
	\hline
	$\Delta$ & spatial discretisation step & 0.5 & mm \\
	$T_s$ & time step & $0.001$ & s\\
	$T$ & number of time steps used in estimation & 0.4 & s\\
	\hline 
\multicolumn{4}{|c|}{\emph{Model}}\\
	\hline
	$\tau$ & synaptic time constant & 0.01 & s$^{-1}$ \\
	$f_{max}$ & maximal firing rate & 10 & spikes.s$^{-1}$\\
	$\varsigma$ & slope of sigmoidal activation function & 0.8 & mV$^{-1}$\\
	$v_0$ & firing threshold & 2 & mV \\
	$\boldsymbol{\theta}$ & vector of connectivity kernel parameters & $\left[\begin{array}{ccc}
	10 &-8 &0.5
	\end{array}
	\right]^{\top}$ & mV.spike$^{-1}$\\
	$\sigma_{\psi_{1}}, \sigma_{\psi_{2}}, \sigma_{\psi_{3}}$ & connectivity kernel width parameters & 1.8, 2.4, 6 & mm\\
	$N$ & number of sensors & 196 & n.a.\\ 
	$\Delta_y$ & distance between adjacent sensors & 1.5 & mm\\
	$\sigma_{m}$ & sensor width parameter & 0.9 & mm \\
	$\Sigma_{\varepsilon}$ & observation noise variance & $0.1 \times I_{N}$ & mm$^2$ \\
	$\sigma_{\gamma}$& disturbance spatial covariance width & 1.3 & mm\\
	$\sigma_{\gamma,t}$ & disturbance temporal variance & 0.1 & mV \\
	\hline 
	\multicolumn{4}{|c|}{\emph{Reduced Model}}\\
	\hline
	$L$ & number of basis functions& 81 & n.a.\\
	$\Delta_{\phi}$ & distance between field basis functions & 2.5 & mm \\
	$\sigma^2_{\phi}$ & Spatial variance of Gaussian in spatial domain & 2.5 & mm$^2$\\
	\hline 
	\multicolumn{4}{|c|}{\emph{Frequency Analysis}}\\
	\hline
	$\rho_y$ & sensor over-sampling parameter & 1 & n.a.\\
	$\rho_\phi$ & field basis function over-sampling parameter & 1 & n.a.\\
	\hline 
	\multicolumn{4}{|c|}{\emph{Estimation}}\\
	\hline
	$\alpha$& determines the spread of sigma points & 0.001 & n.a.\\
	$\beta$& prior knowledge of the sigma points distribution & 2 & n.a.\\
	$\kappa$& scaling parameter $(3-L)$& -78 & n.a.\\
	$\lambda$& scaling parameter & -80.99 & n.a.\\
	\hline
\end{tabular}
\begin{flushleft}Parameters for the neural field model, the model reduction, the frequency analysis and the estimation procedure.
\end{flushleft}
\label{tab:Parameters}
\end{table}
